### 2014-10-22 thesis/method/classification.tex
Outlined K* very briefly

\subsubsection{K*: Instance-based Classifier with Entropic Distance Function}

>>>>

\subsubsection{K*: Instance-based Classifier with Entropic Distance Function}
Cleary and Trigg developed K*, an instance-based classifier that uses entropy
to measure the distances between instances \cite{Cleary1995}. They consider
the distance between two instances to be the complexity of transforming one
into another. Define a sequence of transformations on an instance:
\begin{equation*}
\bar{t}(a) = t_n(t_{n-1}(\ldots t_1(a)\ldots)), \bar{t} \in T
\end{equation*}
where $\bar{t} = t_1,\ldots,t_n$. We can define a probability function $p$
that gives the probabilities of these transformations occurring, and then we
can define a probability function that gives the probabilities of all paths
(transformations) from example $a$ to $b$:
\begin{equation*}
P^*(b|a) = \sum_{\bar{t}\in T:\bar{t}(a)=b} p(\bar{t})
\end{equation*}
Within this framework, we can define transformations for both real-valued and
categorical features, which allows K* to work with all types of features.
The K* function is then defined as:
\begin{equation*}
K^*(b|a) = -\mathrm{log}_2P^*(b|a)
\end{equation*}

To calculate the probability of an instance $a$ being in a class $C$, we sum
the probabilities from $a$ to each instance of $C$, and repeat for each class.
The predicted class will be the one with the highest probability:
\begin{equation*}
P^*(C|a) = \sum_{b\in C} P^*(b|a)
\end{equation*}

We use K* as a comparison to the basic NN algorithm and also as a comparison
to $k$-NN with our distance function.
